### 2023-03-13 resilience.tex
up

If we can express $\downarrow Post( J_j)$ then the question become:
is $Safe \cap \cup_{j} \downarrow Post( J_j) \neq \emptyset$ ?

@@

>>>>

If we can express $\downarrow Post^*( J_j)$ then the question become:
is $Safe \cap \cup_{j} \downarrow Post^*( J_j) \neq \emptyset$ ?

@@

Rather, the question is still
"is $Safe \cap \cup_{j}  Post^*( J_j) \neq \emptyset$ ?"

But maybe we can use $\downarrow Post^*( J_j)$ around here.
